---
title: "Gun Control Chi-Square"
author: "Teresa Fukuda"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Teresa and I'm adding some text here to see if my collaborator, Caio, can get this file. 

I'm excited to travel to orlando to see my parents (Caio 2018) 


Creator (Teresa):

Getting gc_df.csv data, loading the tidyverse, and getting some summary counts

```{r}

library(tidyverse)

gc_df <- read_csv("gc_df.csv")

get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>%
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender) 

rownames(get_guns) <- c("Female", "Male")


```

I'm the collaborator (Caio) and I am going to do chi-square

Is gun control perspectives (as related to access to guns) the same for males and females?

Is there a significant association between sex and gun control recommendations?

Is perception of gun control access independent of sex?

Chi-square

```{r}

guns_prop <- prop.table(as.matrix(get_guns), 1)
guns_prop

# Performing Chi-Square

guns_x2 <- chisq.test(get_guns)
guns_x2


```

Recommended gvmt action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`) = ...., p <0.001)


